heuristic1

### 2018-05-24 R/diagrams/heuristic/heuristic.Rmd
R diagrams for heuristic

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

    for every task:
        1. calculate candidates.
        for each candidate until we run out of candidates or we satisfy task's needs:
            1. find available periods.
            Until we run out of periods:
                1. we check if we can assign it (checking remaining time and elapsed time). 
                    * If we can't: we tag the aircraft as "in need of a maintenance'.
                    * if we can: we assign the task.
                2. After assigning a task: we update the remaining and elapsed times for the aircraft.

@@

    if the aircraft is tagged as 'in need of a maintenance':
        1. we check if we can reserve 6 continous months of maintenance.
            * if we can: we do it (and continue assigining tasks to the aircraft).
            * if we cannot: we go to the next candidate.
        2. After assigning a maintenance: we update the remaining and elapsed times for the aircraft.

<!-- <br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br> -->
## Main python code

I think the code gives an idea of the logic behind it. I only include the code for each mission so we would have to execute this function for each mission (or task).

`task` is the mission to satisfy.

* **candidates**: a list with the universe of aircraft that can be assigned to that task.
* **rem_resources**: remaining aircraft that need to be assigned at each period of the task's duration.
* **periods_task**: intersection of available slots for the aircraft (periods without taks or maintenance) and the task's period's needs.

```python

def fill_mission(self, task):
    dtype = 'U7'
    # get task candidates: we copy the list.
    candidates = self.instance.data['tasks'][task]['candidates'][:]
    # get task periods to satisfy:
    rem_resources = \
        aux.dicttup_to_dictdict(
            self.instance.get_task_period_needs()
        )[task]

    while len(rem_resources) > 0 and len(candidates) > 0:
        # candidate = 'A124'
        candidate = candidates[0]
        # get free periods for candidate
        periods_task = \
            self.get_free_starts(candidate, np.fromiter(rem_resources, dtype=dtype))

        # consider eliminating the resource from the list.
        # if all its periods are 'used'
        if len(periods_task) == 0:
            candidates.pop(0)
            continue
        print('candidate={}\ntask={}\nperiods={}'.format(candidate, task, periods_task))
        maint_period = ''
        # TODO: this is still wrong:
        for start, end in periods_task:
            for period in aux.get_months(start, end):
                result = self.check_set_task(candidate, period, task)
                if not result:
                    maint_period = period
                    break
                rem_resources[period] -= 1
            self.update_time_usage(candidate, period, self.get_next_maintenance(candidate, period), 'rut')

        if maint_period != '':
            # find soonest period to start maintenance:
            maint_start = self.get_soonest_maint(candidate, maint_period)
            if maint_start is None:
                # this means that we cannot assign tasks BUT
                # we cannot assign maintenance either :/
                # we should then take out the candidate:
                candidates.pop(0)
                continue
            maint_end = aux.shift_month(maint_start, 5)
            periods_maint = aux.get_months(maint_start,  maint_end)
            for period in periods_maint:
                self.set_maint(candidate, period)
            self.update_time_maint(maint_start, maint_end)
            next_month = aux.get_next_month(maint_end)
            self.update_time_usage(candidate, next_month, 'ret')
            self.update_time_usage(candidate, next_month, 'rut')

```

>>>>

```{r setup, include=FALSE}
source("heuristic.R")
source("../../functions/params.R")

knitr::opts_chunk$set(echo = FALSE)
path <- paste0(PATHS['r_project'], 'diagrams/heuristic/')
```

@@

    for every task:
        1. calculate candidates.
        for each candidate until we run out of candidates or we satisfy task's needs:
            1. find available periods.
            Until we run out of periods:
                1. we check if we can assign it (checking remaining time and elapsed time). 
                    * If we can't: we tag the aircraft as "in need of a maintenance'.
                    * if we can: we assign the task.
                2. After assigning a task: we update the remaining and elapsed times for the aircraft.
            1. If we tagged the aircraft as in need of maintenances: we update.

@@

    1. we check if we can reserve 6 continous months of maintenance.
        * if we can: we do it (and continue assigining tasks to the aircraft).
        * if we cannot: we go to the next candidate.
    2. After assigning a maintenance: we update the remaining and elapsed times for the aircraft.

## Some graphs

### Main loop

```{r, echo=FALSE}
graph_solve(paste0(path, 'heur_solve.csv'), height=500)
```

This loop just goes over each task and tries to fill each one. Particularly important is the order in which we choose to assign the tasks.

### Fill mission

```{r, echo=FALSE}
graph_fill_mission(paste0(path, 'heur_fill_mission.csv'), height=700)
```

This is the most important loop. It gets a task as input.
It iterates over the candidates, finding available periods to assign the task.
It assigns all possible periods to the task.
At the end, it updates the remaining used and elapsed times.
If it finds a period where the candidate cannot get a task because of flight hours or calendar, it marks the candidate as "in need of maintenance" and tries to assign a maintenance in the correct spot or as soon as possible.

### Assign maintenance

```{r, echo=FALSE}
graph_find_assign_maintenance(paste0(path, 'heur_maints.csv'), height=700)
```

This loop takes as input a resource and a period in need of maintenance. With this information, it tries to find the soonest possible period to get the maintenance. Sometimes it doesn't exist, sometimes it is too late. In this case it exits.

If not, it could be the case that there is a maintenance already scheduled around this dates. In this case, it tries to advance (move) the maintenance in order to do it sooner. If it fails the swap, then it does not assign any maintenance.

Finally, if it's possible it assign the maintenance and updates the remaining used and elapsed times for the periods of the maintenance and the following ones.
